--- 
title: "R語言課程"
author: "林頌堅"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "本課程介紹R語言的基本語法以及一些簡單的應用。"
---

# 前言 {-}

本課程介紹R語言的基本語法以及一些簡單的應用，內容如下：

1. R語言的基本概念與語法
2. 運用R語言進行資料處理
3. Tidyverse簡介
4. 資料視覺化
5. 網路資料抓取 (I)
6. 網路資料抓取 (II)
7. 中文斷詞處理
8. 中文未知詞處理
9. 詞語的共現
10. 文件叢集
11. 主題模型

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
